Interleaved Serial and Decision-Theoretic Planning for High-Level Robot Control

### 2011-03-09 subarchitectures/planner.sa/trunk/src/latex/IJCAI-Workshop/ijcai-workshop.tex
Our workshop attempt.

% File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}

\usepackage{subfig}

\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{positioning}

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\graphicspath{{plots/}}
\include{macros}%

\nocopyright

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

@@

% \title{Interleaved Serial and Decision-Theoretic Planning for High-Level Robot Control}

\title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}
\setcounter{secnumdepth}{0}

@@

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to promote efficient
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small abstract subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We evaluate our approach
in large problems from a realistic robot exploration domain.

@@

@@

%% \section{Propositional Decision-Theoretic Planning}
%% \input{prop-dtp.tex}

\section{Planning Language and Notations}
\input{dtpddl.tex}

>>>>

\typeout{IJCAI Switching Planner Submission}

\documentclass{article}
\usepackage{ijcai11}
\usepackage{times}

\usepackage{subfig}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{positioning}

\usepackage{graphicx}
\graphicspath{{plots/}}
\include{macros}%

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (IJCAI Workshop on Decision Making in Partially Observable, Uncertain Worlds: Exploring Insights from Multiple Communities)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%% \title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}

@@

\title{Interleaved Serial and Decision-Theoretic Planning for High-Level Robot Control}

%% \title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}
\setcounter{secnumdepth}{0}

@@

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to exhibit useful
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We demonstrate our approach
in large problems from a realistic robot exploration domain.

@@

For example, the robot usually knows exactly where it is located on a
topological map, and therefore there are tight constraints about what
regions of the map can be observed, and what regions of the map can be
moved to in an atomic step.

Moreover, we use this domain description to model the action physics
of abstract processes posed to decision-theoretic planning
sessions. Here, we forbid the planner from considering courses of
action that are not {\em known} to be possible to alleviate the
computational burden planning in the abstract process.

The initial abstract process, let's suppose, has two states. The state
where everything assumed is true, and the null state. This has a KL
divergence from the :init term, because we can suppose it uniformly
chooses one concrete state, given the abstract :init states.

As you add propositions to the abstract :init term, then the KL
divergence decreases.

@@

\section{Propositional Decision-Theoretic Planning}
\input{prop-dtp.tex}

\section{Decision-Theoretic PDDL}
\input{dtpddl.tex}
